Dynein project log

### 2016-12-30 thesis_stuff/thesis_stuff.tex
Add average length/time to stepping histograms.

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l | p{3cm} | p{5cm} |}
    \hline
    Ls & Lt & kb & kub & cm & cb & ct & notes & outcome\\\hline
    22.1 & 11.1 & 5000 & 5000 & 23.0 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability is about $10^{-150}$, spring constants too high to allow unbinding\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.023 & 0.023 & 0.023 & trying to find good springs for binding & not rigid enough, kneels over and collides with MTs\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.11 & 0.11 & 0.11 & trying to find good springs for binding & this one seems to keel over, not strong enough springs\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability oscillates around $10^{-9}$, but this one seems to also keel over, so springs not strong enough\\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & trying to find good springs for binding & Looks good, takes lots of steps! Too many?\\\hline
    22.1 & 11.1 & 5000 & 5000 & 4.65 & 4.65 & 4.65 & trying to find good springs for binding & Seems very rigid, but might have the right probabilities\\\hline
  \end{tabular}
\end{center}

>>>>

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l | p{3cm} | p{2cm} | p{5cm} |}
    \hline
    Ls & Lt & kb & kub & cm & cb & ct & $\Big<P(\mbox{unbind per dt})\Big>$ & $\Big<\mbox{step time}\Big>$ & errors\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.02 & 0.02 & 0.02 & NA      & NA     & keeled over after ns \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.11 & 0.11 & 0.11 & $9e-9 $ & 1.7e-4 & keeled over after ns\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.18 & 0.18 & 0.18 & $4e-9 $ & 3.4e-4 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & $3e-9 $ & 2.9e-4 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.58 & 0.58 & 0.58 & $2e-10$ & 3.3e-4 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & $6e-12$ & 8.4e-4 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.74 & 1.74 & 1.74 & $1e-13$ & 3.3e-3 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 2.32 & 2.32 & 2.32 & $7e-16$ & 7.8e-3 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 2.90 & 2.90 & 2.90 & $2e-18$ & ?? & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 3.49 & 3.49 & 3.49 & $5e-21$ & ?? & no error yet\\\hline
    22.1 & 11.1 & 2500 & 5000 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
    22.1 & 11.1 & 1500 & 5000 & 3.32 & 3.32 & 3.32 & ?? & ?? & \\\hline
    22.1 & 11.1 &  500 & 5000 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
    22.1 & 11.1 &  100 & 5000 & 3.32 & 3.32 & 3.32 & ?? & ?? & \\\hline
  \end{tabular}
\end{center}

If the mean stepping rate from Weihong's paper is about 1 step / .1 seconds, then at a dt of $1e-11$s would lead to a desired unbinding
probability of $1e-11s/.1s = 1e-10$. The stepping probability was determined by printing out a random subset of unbinding probabilities
for the bothbound case, then averaging.\\

A more reliable step time determiner is $\Big<\mbox{step time}\Big>$. This number can be determined from the step time histograms.\\
